---
title: '`r params$title`'
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
output:
  pdf_document:
    keep_tex: yes
    toc: yes
    fig_caption: yes
    fig_crop: no
    fig_height: 3.5
    fig_width: 6.5
    includes:
      in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
  word_document:
    reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
params:
  loadRZCs: "`r NULL`"
  outDir: "./OutputFiles"
  title: "Effective N for NMFS Survey Size Compositions"
  species: "BTC"
  bootN: 100
  minYr: 1975
  maxYr: 2017
  minSize: 25
  maxSize: 185
  binSize: 5
  lglZ: 125
  bySex: "`r TRUE`"
  byMaturity: "`r TRUE`"
  byShellCondition: "`r TRUE`"
  verbosity: 0
fontsize: 11pt
---

```{r setup,echo=FALSE, error=FALSE, message=FALSE, warning=FALSE,results='hide'}
  ##dir.top<-"Y:"; ##Windows
  dir.top<-"~";    ##Mac
  dir.TS<-"StockAssessments-Crab/Data/Survey.NMFS.EBS/Current";##could be an input
	path<-file.path(dir.top,dir.TS);
  fn.SD<-"TannerCrab_SurveyStrata.csv";
  fn.CH<-"TannerCrab_HaulData.csv";
  outDir<-params$outDir;
  if (!dir.exists(outDir)) dir.create(outDir);

  figno<-1;
  tblno<-1;

  #load required packages
  require(tcsamSurveyData);
  require(wtsPlots);
  require(tables);
  options(stringsAsFactors=FALSE);

  ##set knitr options for subsequent chunks
  knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, dpi=300);
```

\listoftables

\listoffigures

\clearpage

#Introduction

This report estimates the effective N associated with size compositions from NMFS survey data.

```{r inputs}
  if (!is.null(params$loadRZCs)){
    load(params$loadRZCs);#restore saved variables
  } else {
    ##
    species<-params$species;
    strataType<-'2015';
    minYr<-params$minYr;
    maxYr<-params$maxYr;
  	haulTypes<-NULL;#get ALL haul types for new time series
  	minSize<-params$minSize;#minimum size of individuals to extract
  	cutpts<-seq(from=minSize,to=params$maxSize,by=5);
  
    lglZ<-params$lglZ;#industry-preferred male size
  }
    verbosity<-params$verbosity;##0=off,1=minimal,2=full
      
    ##required preliminary calculations
    codes.TS<-Codes.TrawlSurvey();
    Sum<-function(x){base::sum(x, na.rm=TRUE)};#sum function with na.rm=TRUE
```

The survey data were processed using the following parameters: 

```{r makeTable,results="asis"}
  cap<-"Parameters used to process crab haul data.";
  dfr<-data.frame(Quantity=c(
                    "min size (mm CW)","max size (mm CW)","bin size (mm CW)","strata type","haul types"),
                  Value=as.character(c(
                    minSize,maxSize,binSize,strataType,ifelse(is.null(haulTypes),"all",haulTypes))),stringsAsFactors=FALSE);
  tbl<-as.tabular(dfr);
  latex(tbl,
        options=list(tabular="longtable",
                     toprule=paste0("\\caption{",cap,"} \\\\ \n\\hline"),
                     midrule="\\hline\\\\\n[-2\\normalbaselineskip]\\endhead\\hline\\endfoot\\\\"));
  cat("\n\n");
  rm(dfr,tbl);
```

```{r readDataFiles}
  if (is.null(params$loadRZCs)){
      ##select strata definitions
      tmp0<-read.csv(file.path(path,fn.SD),check.names=FALSE,stringsAsFactors=FALSE)[,1:8];
      names(tmp0)[8]<-"TOTAL_AREA";
      dfr.SD<-selectStrata.TrawlSurvey(tmp0,
      																 species=species,
      																 strataType=strataType,
                                       export=FALSE,
      																 verbosity=verbosity);
  		#load crabhaul files
  		dfr.crabhauls<-NULL;
  		for (f in fn.CH){
  			tmp1<-read.csv(file=file.path(path,f));
  			dfr.crabhauls<-rbind(dfr.crabhauls,tmp1);
  		}
  
      rm(tmp0,tmp1);
  }
```

```{r getData.TrawlSurvey}
  if (is.null(params$loadRZCs)){
      ##select haul data
      dfr.HD<-selectHauls.TrawlSurvey(dfr.SD,
      								                tbl=dfr.crabhauls,
                                      YearRange=c(minYr,maxYr),
                                      export=FALSE,
                                      verbosity=verbosity);
      #select individuals
      dfr.ID<-selectIndivs.TrawlSurvey(dfr.HD,
      								                 tbl=dfr.crabhauls,
                                       sex='ALL',
      								                 shell_condition='ALL',
                                       maturity='ALL',
      								                 calcMaleMaturity=TRUE,
                                       minSize=minSize,
      								                 maxSize=Inf,
                                       export=FALSE,
      								                 verbosity=verbosity);
    rm(dfr.crabhauls);
  }
```

```{r calcResampledSizeCompositions}
  if (is.null(params$loadRZCs)){
    dfrRZCs <- calcResampledSizeComps(N=params$bootN,
                                      tbl_strata=dfr.SD,
                                      tbl_hauls=dfr.HD,
                                      tbl_indivs=dfr.ID,
                                      bySex=params$bySex,
                                      byMaturity=params$byMaturity,
                                      byShellCondition=params$byShellCondition,
                                      byEBS=TRUE,
                                      truncate.low=TRUE,
                                      truncate.high=FALSE,
                                      cutpts=cutpts);
    if (!("SEX" %in% names(dfrRZCs)))             dfrRZCs$SEX<-"all";
    if (!("MATURITY" %in% names(dfrRZCs)))        dfrRZCs$MATURITY<-"all";
    if (!("SHELL_CONDITION" %in% names(dfrRZCs))) dfrRZCs$SHELL_CONDITION<-"all";
  }
```

#Resampled size compositions
The resampled size compositions are presented in this section. 

```{r plotResampledSizeCompositions,results="asis",out.width="6.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  lstRZCs<-plotResampledSizeComps(dfrRZCs);
  caps<-names(lstRZCs$plots)[1:(length(names(lstRZCs$plots))-2)];
  captions<-gsub("Figure &&figno. ","",caps,fixed=TRUE);
  for (p in caps) {print(lstRZCs$plots[[p]])};
  rm(caps)
```

\clearpage

#Effective sample sizes
The resulting effective sample sizes are presented in the following figure and table.

```{r plotEffectiveNs,results="asis",out.height="3.0in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  caps<-names(lstRZCs$plots)[(length(names(lstRZCs$plots))-1):length(names(lstRZCs$plots))];
  captions<-gsub("Figure &&figno. ","",caps,fixed=TRUE);
  for (p in caps) {print(lstRZCs$plots[[p]])};
  rm(caps)
```

\clearpage


```{r printEffNs, results='asis'}
  tbl<-as.tabular(lstRZCs$effN);
  cap<-"Effective sample sizes for size compositions based on bootstrap resampling."
  latex(tbl,
        options=list(tabular="longtable",
                     toprule=paste0("\\caption{",cap,"} \\\\ \n\\hline"),
                     midrule="\\hline\\\\\n[-2\\normalbaselineskip]\\endhead\\hline\\endfoot\\\\"));
  cat("\n\n");
  rm(tbl,cap);
```

```{r saveAll}
  if (is.null(params$loadRZCs)) 
    save(species,minYr,maxYr,minSize,maxSize,binSize,cutpts,lglZ,
         strataType,haulTypes,dfrRZCs,lstRZCs,file="newRZCs.RData");
  write.csv(lstRZCs$effN,file=file.path(outDir,"EffectiveNs.csv"))
```

