---
author: "William Stockhausen"
date: '`r format(Sys.Date(),"%d %B, %Y")`'
output: 
    word_document: 
      reference_docx: '`r system.file("rmd/StylesforRmdDocs.docx",package="wtsUtilities")`'
    pdf_document: 
        toc: TRUE
        fig_width: 6.5
        fig_height: 4.0
        fig_crop: FALSE
        fig_caption: TRUE
        keep_tex: FALSE
    includes:
      in_header: '`r system.file("rmd/StylesforRmdPDFs.sty",package="wtsUtilities")`'
params: 
  species: "Snow crab"
  cpueType: "biomass"
  title: "&&species spatial patterns in the NMFS trawl survey" 
  outPath: "./"
  dataPath: "./"
  strataFile: ""
  haulFiles: ""
  gisPath: NULL
  strataType: "2015"
  minYr: 2016
  maxYr: 2017
  HaulTypes: NULL
  sex: "ALL"
  maturity: "ALL"
  shell_condition: "ALL"
  calcMaleMaturity: FALSE
  aggBySex: FALSE
  aggByMaturity: FALSE
  aggByShellCondition: FALSE
  minSize: 0
  maxSize: '`r Inf`'
  verbosity: 0
title: '`r gsub("&&species",params$species,params$title,fixed=TRUE)`'
fontsize: 11pt
---

```{r init.MakeMaps.Surveys.CPUE.NMFS,echo=FALSE,results='hide'}
##set knitr options for subsequent chunks
knitr::opts_chunk$set(echo=FALSE, error=FALSE, message=FALSE, warning=FALSE, concordance=TRUE, fig.width=6.5, fig.height=7, dpi=300)
##set options
options(stringsAsFactors=FALSE);
```

```{r inputs.MakeMaps.Surveys.CPUE.NMFS}
  fn.SD<-file.path(params$dataPath,params$strataFile);
  fn.CH<-file.path(params$dataPath,params$haulFiles);
    
  gisDir<-params$gisPath;

  outDir<-params$outPath;
  if (!dir.exists(outDir)) dir.create(outDir);

  ##determine crab type
  if (tolower(params$species)=="tanner crab") {species<-"BTC"; crabType<-"Tanner crab";}    else
  if (tolower(params$species)=="snow crab")   {species<-"OTC"; crabType<-"snow crab";}      else
  if (tolower(params$species)=="BKC") {species<-"BKC"; crabType<-"blue king crab";} else
  if (tolower(params$species)=="RKC") {species<-"RKC"; crabType<-"red king crab";}

  verbosity<-params$verbosity;##0=off,1=minimal,2=full
  
  ##required packages
  require(tcsamSurveyData);
  require(ggpubr);

  ##required preliminary calculations
  codes.TS<-Codes.TrawlSurvey();
```

#Introduction

This report creates a time series of maps of `r crabType` CPUE and bottom temperature from the NMFS EBS bottom trawl survey.

The following figure illustrates the base map for subsequent maps of bottom temperature and survey CPUE.

```{r child=system.file("rmd/makeMaps.Surveys.Basemap.Rmd",package="tcsamSurveyData")}
  ##create the basemap for future maps
```

```{r child=system.file("rmd/calcCPUE.Surveys.NMFS.Rmd",package="tcsamSurveyData")}
  ##calculate survey CPUE and environmental data (dfrCPUE.ByXMS and evs.csv)
```


```{r calcEnvVars}
  stns.polys<-surveyGridLayers$grid;
  stns.pnts<-surveyGridLayers$stations;
  #join annual evs to stns.polys by station
  evs.polys<-wtsGIS::mergeDataframeWithLayer(
                                     evs.csv,stns.polys,
                                     dataID="GIS_STATION",geomsID="STATION_ID",
                                     allData=FALSE,duplicateGeoms=TRUE);
  #join annual evs to stns.pnts by station
  evs.pnts<-wtsGIS::mergeDataframeWithLayer(
                                     evs.csv,stns.pnts,
                                     dataID="GIS_STATION",geomsID="ID",
                                     allData=FALSE,duplicateGeoms=TRUE);
  rm(evs.csv,stns.polys);
```

```{r createRasters}
  strWGS84<-wtsGIS::getCRS("WGS84");

  bbext<-tmaptools::bb(basemap[[1]]$bbox);
  evs.grds<-list();
  yrs<-sort(unique(evs.pnts$YEAR));
  for (yr in yrs){
    idx<-(evs.pnts$YEAR==yr)&(!is.na(evs.pnts$BOTTOM_TEMP));
    spdfr<-as(evs.pnts[idx,],"Spatial");#convert sf object to sp object
    evs.grds[[as.character(yr)]]<-wtsGIS::createRasterLayer(spdfr,
                                                            "BOTTOM_TEMP",
                                                            bbext,
                                                            nx=500,ny=500,
                                                            strCRS=strWGS84);
  }
  rm(strWGS84,yr,yrs,idx,spdfr);
```

#Survey CPUE

The following maps present survey CPUE (in biomass) for components of the `r crabType` stock superimposed on bottom temperature at the time of the survey for each year of the NMFS bottom trawl survey.

```{r createPtsCPUE}
    options(stringsAsFactors=FALSE);
    uXMSs<-unique(dfrCPUE.ByXMS[,c("SEX","MATURITY","SHELL_CONDITION")]);
    if (tolower(params$cpueType)=="abundance"){
      value.var<-"numCPUE";
    } else {
      value.var<-"wgtCPUE";
    } 
    pntsCPUE<-NULL;
    for (iXMS in 1:nrow(uXMSs)){
      #cat("Starting iXMS loop ",iXMS,"\n")
      idx<-dfrCPUE.ByXMS$SEX            ==uXMSs$SEX[iXMS];
      idm<-dfrCPUE.ByXMS$MATURITY       ==uXMSs$MATURITY[iXMS];
      ids<-dfrCPUE.ByXMS$SHELL_CONDITION==uXMSs$SHELL_CONDITION[iXMS];
      tmp<-dfrCPUE.ByXMS[idx&idm&ids,];
      if (nrow(tmp)>0){
        dfr<-reshape2::dcast(tmp,formula=YEAR+GIS_STATION+SEX+MATURITY+SHELL_CONDITION~.,
                             fun.aggregate=sum,value.var=value.var);
        names(dfr)[6]<-"value";
        dfrp<-wtsGIS::mergeDataframeWithLayer(dfr,stns.pnts,
                                              dataID="GIS_STATION",geomsID="ID",
                                              allData=FALSE,duplicateGeoms=TRUE);
        #cat("about to bind\n");
        if (is.null(pntsCPUE)) {pntsCPUE<-dfrp;} else {pntsCPUE<-sf:::rbind.sf(pntsCPUE,dfrp);}
        #cat("finished binding ",iXMS,"\n")
      }
    }#-iXMS
    #rm(iXMS,idx,idm,ids,tmp,dfr,dfrp,stns.pnts);
```


```{r createMaps}
  yrs<-sort(unique(pntsCPUE$YEAR));
  ncol<-min(2,nrow(uXMSs)); nrow<-ceiling(nrow(uXMSs)/2);
  if (nrow==1) {nrow=ncol; ncol=1;}
  ngpp<-nrow(uXMSs);
  nyrs<-length(yrs);
  brks<-seq(from=-2,to=8,by=1);
  pal<-wtsUtilities::createColorPalette("jet",n=100);
  maps<-list();
  for (yr in yrs){
    idy<-pntsCPUE$YEAR==yr;
    mx<-max(pntsCPUE$value[idy],na.rm=TRUE);
    cntr<-1;
    mapsXMS<-list();
    for (iXMS in 1:nrow(uXMSs)){
      uXMS<-uXMSs[iXMS,];
      uX<-uXMS$SEX;
      uM<-uXMS$MATURITY;
      uS<-uXMS$SHELL_CONDITION;
      
      uXp<-""; if (uX!="ALL") uXp<-paste0(" ",uX);
      uMp<-""; if (uM!="ALL") uMp<-paste0(" ",uM);
      uSp<-""; if (uS!="ALL") uSp<-paste0(" ",uS);
      label<-tolower(paste0(as.character(yr),":",uMp,uSp,uXp));
      
      idx<-pntsCPUE$SEX==uX;
      idm<-pntsCPUE$MATURITY==uM;
      ids<-pntsCPUE$SHELL_CONDITION==uS;
      tmp<-pntsCPUE[idy&idx&idm&ids,];
      if (verbosity>0) cat("Creating map",iXMS,"for",uX,uM,uS,"using",nrow(tmp),"points\n");
      if (nrow(tmp)>0){
        map <- tcsamSurveyData::gisCreateSurveyMap.CPUE(
                                       basemap=basemap,
                                       cpue=tmp,
                                       raster=evs.grds[[as.character(yr)]],
                                       cpueCol="value",
                                       cpueLabel="CPUE",
                                       cpueColor="blue",
                                       cpueAlpha=0.6,
                                       maxCPUE=mx,
                                       rasterCol="z",
                                       rasterLabel="T (degC)",
                                       rasterPalette=pal,
                                       rasterAlpha=0.6,
                                       rasterBreaks=brks,
                                       rasterLegend=(cntr==min(c(2,ngpp))),
                                       panelLabel=label);
        mapsXMS[[paste(uX,uM,uS)]]<-map;
        cntr<-cntr+1;#increment counter for including legend on map
        rm(map);
      } else {
        if (verbosity>0) cat("--no map created\n")
        mapsXMS[[paste(uX,uM,uS)]]<-NULL;
      }
      rm(uX,uM,uS,uXMS,uXp,uMp,uSp,label,idx,idm,ids,tmp);
    }#-iXMS
    maps[[as.character(yr)]]<-mapsXMS;
    rm(idy,mx,iXMS,mapsXMS,cntr);
  }#-yr
```

```{r printMaps,results="asis",out.width="6.5in",out.height="7.5in",fig.cap=captions,eval.after="fig.cap",fig.pos="H"}
  captions<-vector("character",0);
  for (yr in as.character(yrs)){
    mapsXMS<-maps[[yr]];
    str.expr<-"p<-tmap::tmap_arrange("
    for (iXMS in 1:nrow(uXMSs)){
      uX<-uXMSs$SEX[iXMS];
      uM<-uXMSs$MATURITY[iXMS];
      uS<-uXMSs$SHELL_CONDITION[iXMS];
      str.expr<-paste0(str.expr,"mapsXMS[['",paste(uX,uM,uS),"']],")
    }
    str.expr<-paste0(str.expr,"ncol=",ncol,",nrow=",nrow,",outer.margins=0)");
    if (verbosity>0) cat(str.expr,"\n");
    
    #str.expr<-paste0("tmap::tmap_arrange(maps[[cyr]]$mapIM,maps[[cyr]]$mapIF,maps[[cyr]]$mapMM,maps[[cyr]]$mapMF,ncol=2,nrow=2,outer.margins=0)");
    eval(parse(text=str.expr)[[1]])
    print(p,knit=TRUE);
    cap<-paste0(crabType," CPUE (",params$cpueType,") from the ",yr," NMFS EBS bottom trawl survey.");
    captions<-c(captions,cap);
  }
```



